### 2017-08-25 paper/evaluation.tex
Done with Sec III

After obtaining a list of potential projects, we filtered those
containing a \pomf{} file in the root directory.  A Maven project may
contain several sub-modules with multiple \pomf{} files.\Comment{  We
based our methodology to select experimental subjects on other recent
studies in testing and
debugging~\cite{gligoric-etal-issta2015,perez-etal-icst2017}.}
Also, to avoid bias in our experiments, we executed multiple times all
test suites from our sample set to detect and discard subjects with
\emph{flaky tests}. \Fix{Discuss briefly test flakiness}.
As of August 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. 
From \SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
projects were not Maven or did not have a \pomf{} in the root
directory, \Comment{ were unable to compile due
to missing dependencies,} and \SubjectsGithubNotTestable{} projects
were untestable due to incompatible testing environment.  We also
found \SubjectsGithubFlaky{} projects with ``flaky'' tests.  We
considered those projects but ignored their tests (using JUnit's
\CodeIn{@Ignore} annotation) as to avoid measurement noise.  To detect
those projects, we executed every test suite for three times.  Our
final set of subjects consists of \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
    hosted on \github{}. From this initial sample, we ignored
    \SubjectsGithubNotMaven{} projects without Maven support,
    \SubjectsGithubNotTestable{} untestable projects, and
    \SubjectsGithubFlaky{} projects with flaky tests. We considered
    \numSubjs{} projects to conduct our study.}
\end{figure}

>>>>

After obtaining a list of potential projects, we filtered those
containing a \pomf{} file in the root directory.  A Maven project may
contain several sub-modules with multiple \pomf{} files.
To avoid introducing noise in our experiments, for each project, we
executed the tests \SubjectsReruns{} times to filter projects with
deterministic outcome.
As of August 25th 2017, our search criteria returned \SubjectsGithub{}
subjects.

From these \SubjectsGithub{} downloaded projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory and \SubjectsGithubNotTestable{}
projects were unable to test due to incompatible environment (\eg,
missing required web browser or database management system).
In addition, we identified \SubjectsGithubFlaky{} projects with flaky
tests.
As some of our experiments consist in running tests in a multithreaded
configuration, we ignored these projects as it would be impractical
for us to identify whether a test failed due to a race condition.
Our final set of subjects consists of \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
  \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
  hosted on \github{}. From this initial sample, we ignored
  \SubjectsGithubNotMaven{} projects without Maven support,
  \SubjectsGithubNotTestable{} projects unable to test, and
  \SubjectsGithubFlaky{} projects with flaky tests. We considered
  \numSubjs{} projects to conduct our study.}
\end{figure}

### 2017-08-25 paper/intro.tex
Done with Sec III

The dimensions of analysis we considered in this study are (i)
feasibility, (ii) adoption, (iii) speedup, and (iv) tradeoffs.  The
dimension \emph{feasibility} measures the potential of parallelization
to reduce testing costs.  In the limit, parallelization would be
fruitless if all projects used short-running test suites or if the
execution cost was dominated by a single test case in the suite.  The
dimension \emph{adoption} evaluates how often existing open-source
projects use parallelization schemes and how developers involved in
costly projects (not using test suite parallelization) perceive this
technology.  It is important to measure resistance of practitioners to
the technology and to understand their reasons.  The dimension
\emph{speedups} evaluates the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} in running times.  Finally, the dimension
\emph{tradeoffs} considers the problems in running tests in parallel,
including test flakiness~\cite{luo-etal-fse2014}.  We briefly
summarize our findings in the following.

>>>>

The dimensions of analysis we considered in this study are (i)
feasibility, (ii) adoption, (iii) speedup, and (iv) tradeoffs.  The
dimension \emph{feasibility} measures the potential of parallelization
to reduce testing costs.  In the limit, parallelization would be
fruitless if all projects used short-running test suites or if the
execution cost was dominated by a single test case in the suite.  The
dimension \emph{adoption} evaluates how often existing open-source
projects use parallelization schemes and how developers involved in
costly projects (not using test suite parallelization) perceive this
technology.  It is important to measure resistance of practitioners to
the technology and to understand their reasons.  The dimension
\emph{speedups} evaluates the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} in running times.  Finally, the dimension
\emph{tradeoffs} considers the problems in running tests in parallel.
\Fix{
Non-deterministic outcome for
For tests that change the state of a shared resources (\eg, file or
in-memory collection), data races are likely to occurr.

Data races are likely to occurr in a multithread execution as 
different threare favors data races when Some tests may produce non-deterministic
outcomes in a multithreaded ex when
executed in 
including test flakiness~\cite{luo-etal-fse2014}. A test case with
non-deterministic outcome is also known as ``flaky test''.  are
known as test with non-deterministic outcome and
}
We briefly summarize our findings in the following.
